Figures

### 2019-08-07 figures/08_exploratory_dotplot.Rmd
addd highlight panels for dotplot

dt_tp <- prep_dotplot(dt_tp, "tp") %>%
  dplyr::filter(!str_detect(pretty, "^N ")) %>%
  dplyr::filter(!str_detect(pretty, " N "))

dt_tn <- prep_dotplot(dt_tn, "tn") %>%
  dplyr::filter(!str_detect(pretty, "^P ")) %>%
  dplyr::filter(!str_detect(pretty, " P "))

@@

>>>>

dt_tp <- prep_dotplot(dt_tp, "tp") %>%
  dplyr::filter(!str_detect(pretty, "^N ")) %>%
  dplyr::filter(!str_detect(pretty, " N ")) %>%
  dplyr::filter(!(pretty %in% c("Stream-buffer Ag", 
                                          "N input", "P input")))

dt_tn <- prep_dotplot(dt_tn, "tn") %>%
  dplyr::filter(!str_detect(pretty, "^P ")) %>%
  dplyr::filter(!str_detect(pretty, " P ")) %>%
  dplyr::filter(!(pretty %in% c("Stream-buffer Ag", 
                                          "N input", "P input")))

@@

row_highlight <- function(x, gg){
  # x <- "Fertilizer"
  if(!(x %in% gg$data$pretty)){
    x <- as.character(gg$data$pretty[grep(x, gg$data$pretty)])
  }

  gg + 
    scale_color_manual(values = rep("black", 5)) +
    gghighlight(pretty == x, use_direct_label = FALSE)  
}

dotplot_panel <- function(x){
  plot_grid(NULL, 
plot_grid(row_highlight(x, gg_tp) + theme(legend.position = 0), NULL,
          row_highlight(x, gg_tn), 
          rel_widths = c(1, 0.2, 1), nrow = 1, 
          labels = c("TP", "", "TN"), 
          label_x = c(0.6, 0.5, 0.6), 
          label_y = c(1.05, 1.1, 1.05)), 
ncol = 1, rel_heights = c(0.07, 1))
}

dotplot_panel("Max depth")
dotplot_panel("Baseflow")
dotplot_panel("Corn")
dotplot_panel("Fertilizer")
dotplot_panel("Buffer Ag")
```
